Probabilistic Passphrase Cracking

### 2018-02-07 paper/paper.tex
Paper: committing new pdf, and added a comma in the text

Bonneau and Shutova\cite{payphrase-properties} examined ,,patterns of human
choice in a passphrase-level authentication system deployed by Amazon''. They
,,tested the availability of [over] 100,000 possible phrases at Amazon's
registration page, which prohibits using any phrase already registered by
another user.'' This system allows passphrases as short as two words and
offered no explanation to users regarding what might be secure. Its interface
merely asks for a `phrase' (which is generally a string of {\it logical} words)
and even suggests two-word phrases to use. The conclusion drawn by this paper
is not surprising, given these circumstances: ,,users aren't able to choose
phrases made of completely random words, but are influenced by the probability
of a phrase occurring in natural language. Examining the surprisingly weak
distribution of phrases in natural language, we can conclude that even 4-word
phrases probably provide less than 30 bits of security which is insufficient
against offline attack.'' We consider this low entropy estimation to be
specific for Amazon PayPhrase.

>>>>

Bonneau and Shutova\cite{payphrase-properties} examined ,,patterns of human
choice in a passphrase-level authentication system deployed by Amazon''. They
,,tested the availability of [over] 100,000 possible phrases at Amazon's
registration page, which prohibits using any phrase already registered by
another user.'' This system allows passphrases as short as two words and
offered no explanation to users regarding what might be secure. Its interface
merely asks for a `phrase' (which is generally a string of {\it logical} words)
and even suggests two-word phrases to use. The conclusion drawn by this paper
is not surprising, given these circumstances: ,,users aren't able to choose
phrases made of completely random words, but are influenced by the probability
of a phrase occurring in natural language. Examining the surprisingly weak
distribution of phrases in natural language, we can conclude that even 4-word
phrases probably provide less than 30 bits of security, which is insufficient
against offline attack.'' We consider this low entropy estimation to be
specific for Amazon PayPhrase.
